External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-11 CVPR2017_Review_Unified.tex
ad

\subsection{Comparison with State-of-the-Art Denoising Methods}
%For BM3D, we employ its color version \cite{cbm3d} which would have better performance on color images.

In this section, we compare the proposed method with other state-of-the-art image denoising methods such as BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}. The methods of BM3D \cite{bm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, and TRD \cite{chen2015learning} are designed for removing Gaussian noise. For BM3D and WNNM, the level $\sigma$ of Gaussian noise is very important and is estimated by the method \cite{noiselevel}. The other parameters are set as default. For the methods of MLP, CSF, and TRD, we employ their default parameters settings. Since these methods are designed for grayscale images, we utilize them to denoise the R, G, B channels separately for color noisy images. The Noise Clinic (NC) \cite{noiseclinic} is a blind image denoising method which does not need any noise prior. We also compare with Neat Image (NI), a commercial software for image denoising. Due to its excellent performance, Neat Image (NI) is embedded into Photoshop and Corel PaintShop \cite{neatimage}. The comparisons are performed on the real noisy images from \cite{ncwebsite} and \cite{crosschannel2016}.

\subsubsection{Comparison on the First Dataset \cite{ncwebsite}}

>>>>

\subsection{Comparison with State-of-the-Art Denoising Methods}

We compare the proposed method with state-of-the-art image denoising methods, including CBM3D \cite{bm3d,cbm3d}, WNNM \cite{wnnm}, MLP \cite{mlp}, CSF \cite{csf}, TNRD \cite{chen2015learning}, Noise Clinic (NC) \cite{noiseclinic}, Cross-Channel (CC) \cite{crosschannel2016}, and Neat Image (NI) \cite{neatimage}. Among them, CBM3D, WNNM, MLP, CSF and TNRD are designed based on Gaussian noise model, and they need to know the noise level for denoising. We use the method in \cite{noiselevel} to estimate the noise level for them. All the other parameters in these methods are set as the default ones. Since WNNM, MLP, CSF and TNRD are designed for grayscale images, we use them to denoise the R, G, B channels separately for color noisy images.

Like our method, the NC is a blind image denoising method which does not need any noise prior. The NI is a commercial software for image denoising, which has been embedded into Photoshop and Corel PaintShop \cite{neatimage}. The code of CC is not released but its results on the 15 cropped images are available at \cite{crosschannel2016}. Therefore, we only compare with it on the 15 cropped images from \cite{crosschannel2016}.

\subsubsection{Results on Dataset \cite{ncwebsite}}
